ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-07 paper/paper.tex
update

Below are the parameters we used during training:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance and Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For task 1, we predicted the probability of visiting a particular branch for each customer using $Logarithmic Loss$ as the local evaluation metric.
 We selected top 5 branches with highest probability score. The $cosine@5$ on 30\% of the testing data is $\sim0.65$.

@@

For task 2, we predicted the probability of acquisition for each customer using $AUC$ as the evaluation metric.
The $AUC$ on 30\% of the testing data is $\sim0.719$.

>>>>

\textbf{Table 1} shows the parameters we used during training:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance and Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For task 1, we predicted the probability of visiting a particular branch for each customer using $Logarithmic Loss$ as the local evaluation metric.
 We selected top 5 branches with highest probability score. The best $cosine@5$ on 30\% of the testing data is $\sim0.65$.

@@

For task 2, we predicted the probability of acquisition for each customer using $AUC$ as the evaluation metric.
The best $AUC$ on 30\% of the testing data is $\sim0.719$.
